Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-19 paper.tex
re-write figure 1 caption

We employ this approach in a swarm-like system setting where agents are tasked to cover phenomena detected in their environment. Over time, the agents have to converge over each phenomenon in order to cover it appropriately as illustrated in \Cref{fig:simulations}.
\begin{figure}[t]
	\centering
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{imgs/start.png}
		\caption{Start}
		\label{fig:initial}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{imgs/after.png}
		\caption{After 50 steps}
		\label{fig:after}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{imgs/end.png}
		\caption{After 200 steps}
		\label{fig:end}
	\end{subfigure}
	\caption{Qualitative test results of the proposed approach. 
		The agents go towards the phenomenon and try to cover it without collapsing into a single point.
		the grey area represents the area covered by the agents (last figure on the right).}
	\label{fig:simulations}
\end{figure}

>>>>

We employ this approach in a swarm-like system setting where agents are tasked to cover phenomena detected in their environment. Over time, the agents have to converge over each phenomenon in order to cover it appropriately as illustrated in \Cref{fig:simulations}.
\begin{figure}[t]
	\centering
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{imgs/start.png}
		\caption{Start}
		\label{fig:initial}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{imgs/after.png}
		\caption{After 50 steps}
		\label{fig:after}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{imgs/end.png}
		\caption{After 200 steps}
		\label{fig:end}
	\end{subfigure}
	\caption{Agents (coloured dots) are deployed in an area and have to coordinate to cover the phenomenon. The phenomenon can have varying areas of importance. Over time, the phenomenon will be covered sufficiently without any central controller.
%		
%		Qualitative test results of the proposed approach. 
%		The agents go towards the phenomenon and try to cover it without collapsing into a single point.
%		the grey area represents the area covered by the agents (last figure on the right).
		}
	\label{fig:simulations}
\end{figure}
